A Comparison of Use-Case Based and Checklist- Based Reading: A Controlled Experiment

### 2015-03-12 rmtw/a3/latex8.tex
dsaf

Paradigms in this context will be considered to be those which relate to software development. For example, we would consider Model Driven Software Development to be a development paradigm. In this study we use the term manual coding to describe development without the use of any particular paradigm. The difference being that MDSD is heavily focused upon models and a high level of abstraction for the design of code, whereas manual coding is a standard development process. Our definition of change is not limited to the aforementioned examples, we would consider any changes to development paradigms such as a company wishing to implement processes such as Scrum or introducing Test Driven Development.

@@

\Section{Methodology}

\SubSection{Case Company Description}
The subject case organisation in this study is Ericsson AB. Ericsson operates in the domain of communications technology, their main products are in the domain of mobility, broadband and cloud-based services \cite{a7} \cite{a8}. Ericsson has 117,508 employees (as of September 30, 2014), 25,300 of which work in R\&D (Research and Development). \cite{a7}.

@@

The company was sampled through convenience sampling, and a maximum variation strategy was used. As such, the goal was to include as many companies as possible in this study. Since the study is conducted at a large communications technology company, it indicates that the study may be generalisable to similar companies.

\SubSection{Case Study Design}
The study has been conducted with an exploratory goal in mind. Analysing how Ericsson tackle the problems related to the research questions has been the central part of the study. Due to the exploratory nature of the study, a flexible process design has been used. The study has been carried out using an iterative approach, where the data collected, and the results gathered from analysing the data has been the main driver for shaping and improving the scope and goal of the study. The research has been conducted using a case study approach. The reason for this is that the goal of our study is to analyse how changes are implemented in the context of multi-paradigm development environments in software engineering. This line of thought is supported by Runesson \& Höst in \cite{runeson2009guidelines}. Runesson \& Höst also outline that a case study approach is well-suited for exploratory studies \cite{runeson2009guidelines}. Another reason for conducting this study using a case study approach is that there is little existing research conducted in the area, and that input from industry is vital to the success of the research.

During the initial stage of the study, careful planning was conducted. The two major goals of this phase were to find meaningful objectives with an appropriate design for the research and secondly to facilitate and design the interviews. Although a flexible approach was taken, major effort was spent on planning the study. Most of the planning was related to communicating with Ericsson to facilitate the interviews. A time-line for the interviews was created and established with Ericsson. The objective of analysing change implementation in environments which are split into by two different development activities was also defined during this stage.

\SubSection{Preparation for Data Collection}
The interviewees were sampled using random sampling, with help of a gatekeeper at the company. The reason a gatekeeper was used was to reduce research bias but does eliminate it. Random sampling was performed on official employee records. 15 employees were chosen to be the subjects for the interviews. The subjects were divided into three sub-groups; managers, developers and change agents with 5 of each role being interviewed. The main reason the three different roles were included was to be able to reduce research bias through data triangulation.

The interviewees were selected based on two criterion: they must have been employed at Ericsson for a minimum of 5 years and they must work at the EPG department. 5 years experience was set as a minimum to ensure that all interviewees had experienced a fair number of changes at Ericsson. The reason only employees from EPG were accepted was to ensure that the population was cohesive.

@@

\SubSection{Data Gathering}
The data has mainly been gathered through first degree interviews \cite{lethbridge2005studying}. The interviews were carried out using a mix of open-ended and close-ended questions in combination with a semi-structured approach. The fact that the interviewees had widely differing backgrounds and roles was the main reason for not using a structured approach. A semi-structured approach was chosen over a unstructured approach to be able to obtain results which were closely related to each other. This was performed so that meaningful comparison and analysis could be carried out. Data triangulation was performed to compare and verify the results based on which role the interviewee had. The reason this was done was to reduce risk of, for example, change agents having a positive bias towards previously implemented changes.

@@

\SubSection{Data Analysis}
Data analysis of the interviews was completed in tandem with the data gathering phase. This was performed so that we could iteratively improve upon the data collection process. The main purpose of analysing this data was to generate hypotheses and to refine the proposed research questions. The interviews were analysed by manually reading and comparing answers between the respondents. Spreadsheets and tables were used to provide an overview of the results.

@@

\Section{Threats to Validity}

While designing the study, validity concerns were taken into consideration. The most pressing of which would be the limited scope of the study. The fact that the study only occurred in a subset of Ericsson and not a larger part of the company means that we cannot reliably make any generalities about the results. This is something that could be overcome during a potential triangulation period. For example, further studies could be conducted within Ericsson at other departments which could then be used to strengthen or diminish the results from this study. Furthermore, our study only involved model driven development and manual coding. As such we cannot generalise about the applicability concerning other paradigms.

@@

\item \textbf{General Change}
\begin{itemize}
\item Do you feel that the changes in Ericsson have had a clear plan?
\item How have the goals of the changes been communicated? 
\item What has been the largest obstacle for change?
\item What has been the main driving for change previously?
\item Do you feel that some previously introduced changes do not work well together?
\item Do you feel that the changes are targeted towards individuals or teams? 
\item If you have had previous experience of changes, how is change at Ericsson different? 
\end{itemize}

\item \textbf{Multi-paradigm Change}
\begin{itemize}
\item Do you feel that changes are implemented differently based on what development paradigm is used?
\item Do you feel that the implemented changes work well with both paradigms? 
\item Do you feel that anything has changed in the change strategy since MDSD was introduced? 
\end{itemize}

>>>>

Paradigms in this context will be considered to be those which relate to software development. For example, we would consider Model Driven Software Development to be a development paradigm. In this study we use the term manual coding to describe traditional development where no modeling techniques are used to produce code, i.e. the code is ``hand-written''. The difference being that MDSD is heavily focused upon models and a high level of abstraction for the design of code, whereas manual coding is a standard development process. Our definition of change is not limited to the aforementioned examples, we would consider any changes to development paradigms such as a company wishing to implement processes such as Scrum or introducing Test Driven Development.

@@

\Section{Case Company Description}
The subject case organisation in this study is Ericsson AB. Ericsson operates in the domain of communications technology, their main products are in the domain of mobility, broadband and cloud-based services \cite{a7} \cite{a8}. Ericsson has 117,508 employees (as of September 30, 2014), 25,300 of which work in R\&D (Research and Development). \cite{a7}.

@@

Ericsson has in the last 10 years gone through major changes which relate to way of working, processes, and technical activities and tools. The most major change, which is still ongoing, is the change towards implementing MDSD. Since EPG are still in the process of changing to MDSD, they are now developing their product using two different development paradigms (manual coding and MDSD).

The company and department was sampled through convenience sampling, and a maximum variation strategy was used. As such, the goal was to include as many companies as possible in this study. Since the study is conducted at a large communications technology company, it indicates that the study may be generalisable to similar companies.

\Section{Methodology}
This section will describe the methodology used for the study.

\SubSection{Case Study Design}
The study has been conducted with an exploratory goal in mind. Analysing how Ericsson tackle the problems related to the research questions has been the central part of the study. Due to the exploratory nature of the study, a flexible process design has been used. The study has been carried out using an iterative approach, where the data collected, and the results gathered from analysing the data has been the main driver for shaping and improving the scope and goal of the study.

The methodology used has been case study. The reason for this is that the goal of our study is to analyse how changes are implemented in the context of multi-paradigm development environments in software engineering. This line of thought is supported by Runesson \& Höst in \cite{runeson2009guidelines}. Runesson \& Höst also outline that a case study approach is well-suited for exploratory studies \cite{runeson2009guidelines}. Another reason for conducting this study using a case study approach is that there is little existing research conducted in the area, and that input from industry is vital to the success of the research.

During the initial stage of the study, careful planning was conducted. The two major goals of this phase were to find meaningful objectives with an appropriate design for the research and secondly to facilitate and design the interviews. Although a flexible approach was taken, major effort was spent on planning the study. Most of the planning was related to communicating with Ericsson to facilitate the interviews. A time-line for the interviews was created and established with Ericsson. The objective of analysing change implementation in environments which are split into by two different development activities was also defined during this stage. The case study protocol \cite{brereton2008using} developed and used during this phase can be seen in Table 1. The protocol can be viewed as a high-level timeline for our study.

\begin{table}
	\centering
	\begin{tabular}[Ht]{|l|p{3cm}|p{3.5cm}|}
	\hline
	\textbf{Phase} & \textbf{Activity} & \textbf{Description} \\
	\hline
	1 & Background & Identify related work and research questions \\
	\hline
	2 & Case Study Design & Design the case study, identify object of the study \\
	\hline
	3 & Case Selection & Define criteria for case selection \\
	\hline
	4 & Roles and Responsibilites & Plan and decide roles and responsibilites for researchers \\
	\hline
	5 & Data Collection & Design the data collection phase \\
	\hline
	6 & Data Analyis & Design the data analysis phase \\
	\hline
	7 & Validity & Design plan for how to reduce validity threats \\
	\hline
	8 & Remaining Validity & Identify remaining threats to validity \\
	\hline
	9 & Design Reporting & Identify target audience \\
	\hline
	10 & Schedule & Design a schedule and estimate time for each phase \\
	\hline

	\hline
	\end{tabular}
	\caption{Case Study Protocol}
\end{table}

\SubSection{Preparation for Data Collection}
The interviewees were sampled using random sampling, with help of a gatekeeper at the company. The reason a gatekeeper was used was to reduce research bias. Random sampling was performed on official EPG employee records. Before the records were sampled, the gatekeeper excluded employees which have worked less than 5 years at Ericsson. 5 years experience was set as a minimum to ensure that all interviewees had experienced a fair number of changes at Ericsson. 15 employees were chosen to be the subjects for the interviews. The subjects were divided into three sub-groups; managers, developers and change agents with 5 of each role being interviewed. The main reason the three different roles were included was to be able to reduce bias correlating with roles. The implemented changes might also have different effects on different roles, and thus might provide valuable insight to the study.

@@

\SubSection{Data Gathering}
The data has mainly been gathered through first degree interviews \cite{lethbridge2005studying}. The interviews were carried out using a mix of open-ended and close-ended questions in combination with a semi-structured approach. The fact that the interviewees had widely differing backgrounds and roles was the main reason for not using a structured approach. A semi-structured approach was chosen over a unstructured approach to be able to obtain results which were closely related to each other. This was performed so that meaningful comparison and analysis could be carried out. The data was analysed based on which role the interviewee had. The reason this was done was to reduce risk of, for example, change agents having a positive bias towards previously implemented changes.

@@

\SubSection{Data Analysis}
Data analysis of the interviews was initially carried out in tandem with the data gathering phase. This was performed so that we could iteratively improve upon the data collection process. The main purpose of analysing this data was to generate hypotheses and to refine the proposed research questions. The interviews were analysed by manually reading and comparing answers between the respondents. Spreadsheets and tables were used to provide an overview of the results.

@@

\SubSection{Threats to Validity}
While designing the study, validity concerns were taken into consideration. The most pressing of which would be the limited scope of the study. The fact that the study only occurred in a subset of Ericsson and not a larger part of the company means that we cannot reliably make any generalities about the results. For example, further studies could be conducted within Ericsson at other departments which could then be used to strengthen or diminish the results from this study. Furthermore, our study only involved model driven development and manual coding. As such we cannot generalise about the applicability concerning other paradigms.

@@

\item \textbf{General Change}
\begin{itemize}
\item How do you think the goals for the changes are defined?
\item How have the goals of the changes been communicated? 
\item What has been the largest obstacle for change?
\item What has been the main driving for change previously?
\item Do you feel that some previously introduced changes do not work well together?
\item Do you feel that the changes are targeted towards individuals or teams? 
\item If you have had previous experience of changes, how is change at Ericsson different? 
\end{itemize}

\item \textbf{Multi-paradigm Change}
\begin{itemize}
\item Do you feel that changes are implemented differently based on what development paradigm is used?
\item Do you feel that the implemented changes work well with both paradigms? 
\item Do you feel that anything has changed in the change strategy since MDSD was introduced? 
\item Do you think changes have been more effective after MDSD was introduced? 
\item How do you think MDSD has affected ongoing changes?
\item How do you think change should be designed in multi-paradigm environments?
\item Which changes do you feel should only be adopted in MDSD/manual coding teams?
\item Which changes do you feel should be adopted for both MDSD and manual coding teams?
\end{itemize}

### 2015-03-12 rmtw/a4/latex8.tex
dsaf

\Section{Methodology}
This section will describe which statistical tests were used, and why. The level of significance used for all tests is 0.05. The results have been analysed using a descriptive approach together with a statistical approach.

\SubSection{Tests Used for H\textsubscript{Eff} and H\textsubscript{Rate}}
Initially, Kolmogorov-Smirnov (KS) Goodness-of-Fit and Shapiro-Wilks (SW) tests were used to determine if the assumption of normality could be held for the data set. The data used for the tests was the number faults found by each participant. The reason this data was chosen was that it directly correlates to the data used in H\textsubscript{Eff} and H\textsubscript{Rate}. No data points were removed from the data set before performing any tests for H\textsubscript{Eff} or H\textsubscript{Rate}. The reasoning for this was that the hypotheses only concern number of occurrences and not the qualitative attributes of the data. This means that data points which, for example, contained ``incorrect'' \textit{Item numbers} were still used in the calculation.

@@

The next step was to perform an outlier test. The method used was boxplots. As seen in Figure 3 and 4, no outliers were detected and thus no data points were removed in the tests performed.

@@

To determine if the inspection processes find different risks, we looked at the total frequency of the types of risks found. We decided to use the risk type of the fault as opposed to using the class of fault (Missing, Wrong) as the fault type had more categories to chose from (A,B,C). We chose not to use the section in which the data was located and the item number as the data were mostly incomplete or incorrect.

The frequency of A, B and C risks found were tabulated against the inspection groups which found them. Any response that was not not applicable (NA) was discarded from the table. An example of this is found in table 3. In order to determine if they do find the same risks, a Chi-Square (CS) test of independence was performed on the tabulated results. The reason the CS was used was primarily because the data we wished to use were categorical and the frequency of each category was at least 5. Other tests, such as Fishers Exact Test were not applicable, for example, our table was greater than 2x2 rows and Fishers test should only be used for tables that are 2x2 in size.

@@

\Section{Results}
This section will cover the results of the experiment. The results for H\textsubscript{Eff} and H\textsubscript{Rate} are described in the same sub-sections, since the results are similar and since the results both are relative to the number of average faults found.

\subsection{Results for H\textsubscript{Eff} and H\textsubscript{Rate}}
Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum test was chosen instead of the Student's T-test as the final test. The data used for the WMW test was the efficiency of each participant. The result of the WMW test was W=250, p=0.1063 and with the significance level of 536, thus the null hypothesis H\textsubscript{0 Eff} is rejected.

The same test was chosen for H\textsubscript{Rate}, based on the same reasoning. The result of the WMW test for H\textsubscript{Rate} was W=250, p=0.1063 and with the significance level of 536 thus the null hypothesis H\textsubscript{0 Rate} is rejected.

As evident from the tests, and as can be seen in Table 4, the results for H\textsubscript{Eff} and H\textsubscript{Rate} are similar. Both show that there is a difference between the two inspection methods, and both show greater results for CL. Table 3 shows that UC finds more faults of risk type A and C, but the fact that the CL data contained 18 more faults that contained an incorrect fault risk entry could be a possible explanation for that.

\subsection{Results for H\textsubscript{Fault}}
As mentioned previously, the CS test was used to determine if the reviewers discovered the same frequency of results. The result of the X\textsuperscript{2} was 1.5998, generating a p-value of 0.4494. For v=2 and alpha = 0.05, the upper critical value is 5.991 and the lower critical value is 0.103. Since 1.5998 is \textless 5.991 and \textgreater 0.103, the alternative hypothesis of the CS test is rejected. Since \textsubscript{0 Fault} and \textsubscript{1 Fault} are inverted compared to the hypothesis of the CS test, the null hypothesis of H\textsubscript{Fault} is rejected.

When looking at the results of the study, UC appears to find many more class A and class B faults than CL, however, CL finds more class B faults. However, on average, the CL reviews found more faults overall and as such could be considered more effective than UC. This, coupled with the rejection of the H\textsubscript{Fault} null hypothesis, provides ample evidence that the review techniques do differ in which faults they are finding. A suggestion for a follow up study would be to determine why one inspection process finds faults that the other does not and if this affects the effectiveness of that process.

\begin{table}
	\centering
	\begin{tabular}[ht]{|l|l|l|}
	\hline
	& UC & CL \\
	\hline
	Mean(Total faults found) & 4.61 & 5.48 \\
	\hline
	Median(Total faults found) & 3.5 & 5.0 \\
	\hline
	Detection Rate & 0.12 & 0.14 \\
	\hline
	\end{tabular}
	\caption{Results Summary}
\end{table}

The slight variation in favour of the CL technique is further evidence that CL is more efficient and therefore more effective than UC.

@@

\Section{Acknowledgement}
John had the main responsibility for sections 3.2, 4.2. William had the main responsibility for sections 3.1, 4.1. The research questions were written together. We have, however, worked on all sections jointly - and all sections have been reviewed by both William and John. The testing has been done using a ``pair-testing'' approach.

Note: We were a bit unsure whether to only analyse the tests with help of the p-value or analysing the p-value together with test result and critical-value was the correct. We decided to do the latter and would like feedback on this.

>>>>

\Section{Methodology}
This section will describe which statistical tests were used, and why they were chosen. The level of significance ($\alpha$) used for all tests is 0.05. The results have been analysed using a descriptive approach together with a statistical approach.

\SubSection{Tests Used for H\textsubscript{Eff} and H\textsubscript{Rate}}
Initially, Kolmogorov-Smirnov (KS) Goodness-of-Fit and Shapiro-Wilks (SW) tests were used to determine if the assumption of normality could be held for the data set. The data used for the tests was the number faults found by each participant. The reason this data was chosen was that it directly correlates to the data used in H\textsubscript{Eff} and H\textsubscript{Rate}. No data points were removed from the data set before performing any tests for H\textsubscript{Eff} or H\textsubscript{Rate}. The reasoning for this was that the hypotheses only concerned with the number of occurrences and not the qualitative attributes of the data. This means that data points which, for example, with ``incorrect'' \textit{Positions} were still used in the calculation.

@@

The next step was to perform an outlier test. To identify these, boxplots were generated and reviewed. As seen in Figure 3 and 4, no outliers were detected and thus no data points were removed in the subsequent tests.

@@

To determine if the inspection processes find different risks, we looked at the total frequency of the types of risks found. We decided to use the risk type of the fault as opposed to using the class of fault (Missing, Wrong) as the fault type had more categories to choose from (A,B,C). We chose not to use \textit{Position} as the data were mostly incomplete or incorrect.

The frequency of A, B and C risks found were tabulated against the inspection groups which found them. Any response that was not applicable (NA) was discarded from the table. An example of this is found in Table 3. In order to determine if they do find the same risks, a Chi-Square (CS) test of independence was performed on the tabulated results. The reason the CS test was used was primarily because the risk data were categorical and the frequency of each category was at least 5. Other tests, such as Fishers Exact Test were not applicable, for example, as our table was greater than 2x2 rows and Fishers test should only be used for tables that are 2x2 in size.

@@

\Section{Results}
This section will cover the results of the experiment. The results for H\textsubscript{Eff} and H\textsubscript{Rate} are described in the same sub-section, since the results are similar and since the results both hypotheses are relative to the number of average faults found.

\subsection{Results for H\textsubscript{Eff} and H\textsubscript{Rate}}
Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum test was performed instead of the Student's T-test as the test for H\textsubscript{Eff}. The data used for the WMW test was the efficiency of each participant. The result of the WMW test was p=0.1063 and thus the alternative hypothesis, H\textsubscript{1 Eff}, is rejected.

The same test was chosen for H\textsubscript{Rate}, based on the same reasoning. The result of the WMW test for H\textsubscript{Rate} was p=0.1063 and thus H\textsubscript{1 Rate} is rejected.

As evident from the tests, and as can be seen in Table 4, the results for H\textsubscript{Eff} and H\textsubscript{Rate} are similar. Both show that there is a slight difference between the two inspection methods, and there is a slight better result for CL. The results are, however, not statistically significant enough for the null hypotheses to be rejected. Table 3 shows that UC finds more faults of risk type A and C, but the fact that the CL data contained 18 more faults that contained an incorrect fault risk entry is be a possible explanation for this result.

\subsection{Results for H\textsubscript{Fault}}
As mentioned previously, the CS test was used to determine if the reviewers discovered the same frequency of results. The result of the $\chi $ \textsuperscript{2} was 1.5998, generating a p-value of 0.4494. For $\nu$=2 and $\alpha$=0.05, the upper critical value is 5.991 and the lower critical value is 0.103. Since 1.5998 is \textless 5.991 and \textgreater 0.103, the alternative hypothesis of the CS test is rejected. Since H\textsubscript{0 Fault} and H\textsubscript{1 Fault} are inverted compared to the hypothesis of the CS test, the null hypothesis of H\textsubscript{Fault} is rejected.

When looking at the results of the study, UC appears to find more class A and class B faults than CL, however, CL finds more class B faults. However, on average, the CL reviews found more faults overall and as such could be considered more effective than UC. This, coupled with the rejection of the H\textsubscript{Fault} null hypothesis, provides ample evidence that the review techniques do differ in which faults they are finding.

\begin{table}
	\centering
	\begin{tabular}[ht]{|l|l|l|}
	\hline
	& UC & CL \\
	\hline
	Mean(Total faults found) & 4.62 & 5.48 \\
	\hline
	Median(Total faults found) & 3.5 & 5.0 \\
	\hline
	Detection Rate & 0.12 & 0.14 \\
	\hline
	\end{tabular}
	\caption{Results Summary}
\end{table}

@@

\Section{Acknowledgement}
John had the main responsibility for sections 3.2, 4.2. William had the main responsibility for sections 3.1, 4.1. The research questions were written together. We have, however, worked on all sections jointly - and all sections have been reviewed by both William and John. The testing has been done using a ``pair-testing'' approach. \newline

\noindent
\textbf{Notes:}
\begin{itemize}
\item We were a bit unsure whether to only analyse the tests with help of the p-value or analysing the p-value together with test result and critical-value was correct. We decided to do the latter and would like feedback on this. 
\item We ended up creating our own research questions based on the alternative hypotheses, since they were not included in Experiment\_Design.pdf. Hopefully this is what you were looking for.
\end{itemize}
